\documentclass[12pt]{article}

\usepackage{verbatim}

\title{Game Dev Assignment 4}
\author{Tif, Ashley, Ian, Julian, Andrew}
\date{Nov. 14, 2012}

\begin{document}
    \maketitle
    \begin{comment}
    \section{Overview}
        you're a robot dog, trusting of your masters and they tell you they're testing you but they're actually setting you up to fail and they're testing their trap systems

        flaw is that you're very trusting and loyal, which would normally be great, but they are actually using you as a disposable robot to test traps

        more and more dead robots as you get along

        they set you up to do a test which will kill you if you do the obvious route, grumpy if you ``pass'' the test.


        alternate, they write you off as you make it through challenges, infiltrated later
    \end{comment}
    \section{Overview}
        You are a robot dog, used for testing automated security systems.  Your masters are testing their new security system and are requiring you to attempt to make your way past various obstacles so they can find the holes in their system.  These challenges lead the player to be unable to, for example, jump in a level, when the obvious answer is jumping across the pit.
        
        As you progress, foiling each layer of the system, your masters become more and more discouraged, and eventually replace their security system with one that is too intensive which secretly takes control and prevents them from using their facilities.  Their trait is that they are paying close attention to these results and don't have high enough confidence in their abilities and therefore contract the job out too a firm who secretly infiltrates them while installing the system.  The dog then must break in to the facility to deactivate the new system.

        you're flawed, too good at defeating security, destroy it by accident while testing it; they rebuild it and lock their keys inside and you need to break in again to disable the security
\end{document}
